### 2021-05-24 concurrency/docs/theory/theory.tex
add a few more lines

\newcommand{\Inv}{Inv}
\newcommand{\inv}{inv}
\newcommand{\HTInv}{HTInv}
\newcommand{\Heap}{Heap}
\newcommand{\htinv}{htinv}
\newcommand{\inlinehoare}[1]{{\color{blue}\left\{#1\right\}}}

@@

\begin{align*}
  &\inlinehoare{\active(\kappa) * \borrow{\kappa}{\dboxed{ht.entries}^\gamma}
      * \dboxed{k \hashto v_0}^\gamma \land KeyNotInRange(ht.entries, k, i)}\\
  &\AcquireShared(ht.rwlocks[i]);\\
  &\inlinehoare{\active(\kappa) * \borrow{\kappa}{\dboxed{ht.entries}^\gamma}
      * \dboxed{k \hashto v_0}^\gamma \land KeyNotInRange(ht.entries, k, i)
      * \SharedGuard\left( (i \entryto c, ht.entries[i] \pointsto c) \right) }\\
  &\langlet r = (\langmatch~ !ht.table[i] ~\langwith\\
  &~~~~ |~ \None \Rightarrow \None\\
  &~~~~ |~ \Some~(k_0,v_0) \Rightarrow
      \langif~ k = k_0 ~\langthen~ Some(v_0) ~\langelse~ \QueryIter(ht,k,i+1)\\
  &\langend) ~\langin\\
  &\ReleaseShared(ht.rwlocks[i]);\\
  &r\\
  &\inlinehoare{\active(\kappa) * (k \hashto v_0) \land v = v_0}
\end{align*}

>>>>

\newcommand{\Inv}{Inv}
\newcommand{\inv}{inv}
\newcommand{\HTInv}{HTInv}
\newcommand{\Heap}{Heap}
\newcommand{\htinv}{htinv}
\newcommand{\inlinehoare}[1]{{\color{blue}\left\{#1\right\}}}
\newcommand{\inlinehoarel}[1]{{\color{blue}\left\{#1\right.}}
\newcommand{\inlinehoarer}[1]{{\color{blue}\left.#1\right\}}}

@@

\begin{align*}
  &\inlinehoare{\active(\kappa) * \borrow{\kappa}{\dboxed{ht.entries}^\gamma}
      * \dboxed{k \hashto v_0}^\gamma \land KeyNotInRange(ht.entries, k, i)}\\
  &\AcquireShared(ht.rwlocks[i]);\\
  &\inlinehoare{\active(\kappa) * \borrow{\kappa}{\dboxed{ht.entries}^\gamma}
      * \dboxed{k \hashto v_0}^\gamma \land KeyNotInRange(ht.entries, k, i)
      * \SharedGuard\left( (i \entryto c, ht.entries[i] \pointsto c) \right) }\\
  &\inlinehoarel{\active(\kappa) * \borrow{\kappa}{\dboxed{ht.entries}^\gamma}
      * \dboxed{k \hashto v_0}^\gamma \land KeyNotInRange(ht.entries, k, i)}\\
  &\inlinehoarer{~~~~
      * \active(\kappa_0) * \borrowed\left(\kappa_0, \SharedGuard\left( (i \entryto c, ht.entries[i] \pointsto c) \right) \right)
      * \borrow{\kappa_0}{\SharedGuard\left( (i \entryto c, ht.entries[i] \pointsto c) \right) }}\\
  &\langlet r = (\langmatch~ !ht.table[i] ~\langwith\\
  &~~~~ |~ \None \Rightarrow \None\\
  &~~~~ |~ \Some~(k_0,v_0) \Rightarrow
      \langif~ k = k_0 ~\langthen~ Some(v_0) ~\langelse~ \QueryIter(ht,k,i+1)\\
  &\langend) ~\langin\\
  &\ReleaseShared(ht.rwlocks[i]);\\
  &r\\
  &\inlinehoare{\active(\kappa) * (k \hashto v_0) \land v = v_0}
\end{align*}
